PM Mungbean meta-analysis

### 2021-02-01 02_Preliminary_analysis.Rmd
remove proportionl grain yield inspection and small edits

```{r PropiDoseEffect}
PM_MB_dat %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   labs(label = "Yield for each respective propiconazole dose",
        caption = "Facets indicate the number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ylab("Yield gain proportially\nto the no spray control") +
   facet_grid(cols = vars(total_fungicide))
```

@@

```{r JadeYieldLoss}
PM_MB_dat %>%
   filter(year == "2016",
          host_genotype == "Jade") %>%
   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control",
                                TRUE ~ "FungicideTreated")) %>%
   group_by(location, Treatment) %>%
   summarise(
      trial_ref = trial_ref,
      location = location,
      year = year,
      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
      .groups = "drop"
   ) %>%
   distinct() %>%
   pivot_wider(names_from = Treatment, values_from = Yield) %>%
   mutate(Diff = FungicideTreated - control) %>%
   mutate(percent = (Diff / FungicideTreated) * 100) %>%
   select(trial_ref,
          location,
          year,
          control,
          FungicideTreated,
          percent,
          Diff)
```

## Summary of disease incidence effect on yields

This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.
The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.

>>>>

```{r PropiDoseEffect}
PM_MB_dat %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = grain_yield.t.ha.)) +
   xlab("Dose (g ai/ha)") +
   labs(label = "Yield for each respective propiconazole dose",
        caption = "Facets indicate the number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ylab("Grain yield t / ha") +
   facet_grid(cols = vars(total_fungicide))
```

@@

```{r JadeYieldLoss}
PM_MB_dat %>%
   filter(year == "2016",
          host_genotype == "Jade") %>%
   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
                                TRUE ~ "FungicideTreated_yield")) %>%
   group_by(location, Treatment) %>%
   summarise(
      trial_ref = trial_ref,
      location = location,
      year = year,
      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
      .groups = "drop"
   ) %>%
   distinct() %>%
   pivot_wider(names_from = Treatment, values_from = Yield) %>%
   mutate(Diff = FungicideTreated_yield - control_yield) %>%
   mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
   select(trial_ref,
          location,
          year,
          control_yield,
          FungicideTreated_yield,
          percent,
          Diff)
```
